Subject-specific curves for time series forecasting of smart meter demand

### 2020-04-01 sscts-paper-1-wp.Rmd
Fixed reference

Few papers have attempted to assess the impact of differences in building characteristics using statistical methods and smart meter data. To the author's knowledge, only a previous paper by @Roach2019-ss has looked into this using mixed effects models. Whereas that paper focused on estimating demand impact profiles for building attributes at different times of the year, this paper focuses on improving forecast accuracy and producing scenario analyses by estimating the expected change in time series conditional on the building attributes.

@@

Building attribute data describes different characteristics of each building. The data are Boolean and indicate if a particular attribute is absent or present. A previous paper [@Roach2019-ss] that examined important drivers of commercial office building demand identified the following attributes as relevant:

@@

For a more detailed discussion of each of these attributes refer to @Roach2019-ss.

>>>>

Few papers have attempted to assess the impact of differences in building characteristics using statistical methods and smart meter data. To the author's knowledge, only a previous paper by @Roach2019-ch has looked into this using mixed effects models. Whereas that paper focused on estimating demand impact profiles for building attributes at different times of the year, this paper focuses on improving forecast accuracy and producing scenario analyses by estimating the expected change in time series conditional on the building attributes.

@@

Building attribute data describes different characteristics of each building. The data are Boolean and indicate if a particular attribute is absent or present. A previous paper [@Roach2019-ch] that examined important drivers of commercial office building demand identified the following attributes as relevant:

@@

For a more detailed discussion of each of these attributes refer to @Roach2019-ch.
